---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# documentNumbering

<!-- badges: start -->
<!-- badges: end -->

The goal of `documentNumbering` is to provide figure and table numbering in Rmd / qmd output formats that don't normally provide figure numbers.
This package exists as an alternative to the number referencing provided by the [bookdown package](https://bookdown.org/yihui/rmarkdown-cookbook/figure-number.html).

## Installation

You can currently install from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("rmflight/documentNumbering")
```

## Examples

### R6 Object

The way to use this is the actual {R6} object, `dn_counter` that gets updated, and contains all the information for printing, and which you initialize with whatever values you want for a prefix, and a character to use to replace any spaces in the prefix.

```{r example_r6}
library(documentNumbering)
# a normal example in a main manuscript
my_counter = dn_counter$new("Figure ", "_")
my_counter
# one where you want an "S" in front of the number
s_counter = dn_counter$new("Figure ", "_", "S")
s_counter
```

When it is initialized, there are no counts, and no names for the counts.


### Increment the Count

```{r increment_count}
my_counter$increment("descriptive_name")
my_counter

s_counter$increment("a_name")
s_counter
```

Here we can see that the count now includes a "1", and 
In the case of the `s_counter`, we can now see that the "S" gets added directly to the counter, and the count is actually stored as a character.

We can also add multiple items at a time:

```{r}
#| label: increment_multiple
my_counter$increment(c("b_name",
                       "c_name"))
```

### Paste in Text

Now we want to refer to it in the text, we can do:

```{r show_output}
my_counter$label_text("descriptive_name")
```

### Refer to Multiple

Often we want to refer to multiple figures at once:

```{r multiple}
# add another entry first
my_counter$increment("descriptive_2")
my_counter$label_text(c("descriptive_name", "descriptive_2"))
```

### Change Name

If we've supplied the incorrect name, we can change it if you really want (I doubt this comes up much, but it's there).

```{r change_name}
my_counter$rename("descriptive_name", "descriptive_1")
my_counter
```

### File Paths

In addition to just using the counter, there is the ability to modify the file names of the figures generated.
This is particularly useful if you are creating figure files for a manuscript.
If you set `keep_md: true` in the yaml header, and then you can add a custom figure processor, `modify_path`, which is one of the functions in the `dn_counter` object you instantiate:

For `rmarkdown`:

```yaml
output:
  word_document:
    keep_md: true
```

For `quarto`:

```yaml
output:
  docx:
    keep-md: true
```

```{r example_processor_r6}
figure_count = dn_counter$new()
knitr::opts_chunk$set(fig.process = figure_count$modify_path)
figure_count$increment(c("plot", "plot2"))
```

And then to rename the figure file, you set the chunk **label** to be the same as the figure number you want to access:

````
```{r}
#| label: plot
plot(rnorm(100), rnorm(100))
```
````

Alternatively:

````
```{r plot2}
plot(rnorm(100), rnorm(100))
```
````

The figure file will be prepended with `Figure_1-` in the output directory that is generated, which makes it much easier to refer to when uploading files or sharing them with collaborators.
